SecureIt: home security\\ via Android application

### 2013-01-02 relazioni/wireless/paper.tex
Ultime modifiche relazione reti wireless

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage{longtable}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{color}
\usepackage{caption}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\linewidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{listings}
\lstset{ %
  basicstyle=\footnotesize,           % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1, each line 
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},      % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  %frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=t,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{blue},          % keyword style
  commentstyle=\color{dkgreen},       % comment style
  stringstyle=\color{mauve},         % string literal style
  escapeinside={\%*}{*)},            % if you want to add a comment within your code
  morekeywords={*,...}               % if you want to add more keywords to the set
}

@@

\section{\textbf{Introduction}}

The aim of the application development was not only the creation of a home security system but also the discovery of phone capabilities. In fact operations performed by the application are complex and really resource needful:
\begin{itemize}
	\item Accelerometer to detect orientation and shake
	\item Camera to detect motion processing frames
	\item Microphone to detect environmental sound level
	\item Wifi or 3G connectivity to upload images and audio
	\item GPS to get current location
	\item Bluetooth to upload location in absence of connectivity
	\item In app encryption in order to securely authenticate the user
\end{itemize}

@@

\subsection{\textbf{No pairing}}
Android offers two ways for creating a bluetooth server socket: \texttt{listenUsingRfcommWithServiceRecord} e \texttt{listenUsingInsecureRfcommWithServiceRecord}. The first method creates a server socket listening for incoming connections created via \texttt{createInsecureRfcommSocketToServiceRecord} and needs an explicit pairing of two devices with user acceptance. The second method instead allows to manage incoming connection created with \texttt{} that do not require pairing with user acceptance.\\

@@

@@

\bibitem{}
B. Clifford Neuman and Theodore Ts'o (September 1994) Kerberos: An Authentication Service for Computer Networks.  IEEE Communications 32. \\

>>>>

\documentclass[conference, 11pt]{IEEEtran}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage{longtable}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{color}
\usepackage{caption}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\linewidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{listings}
\lstset{ %
  basicstyle=\footnotesize,           % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1, each line 
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},      % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  %frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=t,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{blue},          % keyword style
  commentstyle=\color{dkgreen},       % comment style
  stringstyle=\color{mauve},         % string literal style
  escapeinside={\%*}{*)},            % if you want to add a comment within your code
  morekeywords={*,...}               % if you want to add more keywords to the set
}

@@

\section{\textbf{Introduction}}
Traditional surveillance systems rely on ad hoc and proprietary solutions and have weaknesses like poor mobility, high costs and low flexibility. Current smartphones spread makes possible to exploit these devices to protect our homes.\\

The developed application exploits phone's hardware in order to offer a traditional survellance system services.\\

The aim of the application development was not only the creation of a home security system but also the discovery of phone capabilities.

\section{\textbf{Application overview}}
Operations performed by the application are complex and really resource needful:
\begin{itemize}
	\item Accelerometer to detect orientation and shake
	\item Camera to detect motion processing frames
	\item Microphone to detect environmental sound level
	\item Wifi or 3G connectivity to upload images and audio
	\item GPS to get current location
	\item Bluetooth to upload location in absence of connectivity
	\item In app encryption in order to securely authenticate the user
\end{itemize}

@@

\subsection{\textbf{No pairing}}
Android offers two ways for creating a bluetooth server socket: \texttt{listen\allowbreak Using\allowbreak Rfcomm\allowbreak WithServiceRecord} e \texttt{listen\allowbreak Using\allowbreak Insecure\allowbreak RfcommWithServiceRecord}. The first method creates a server socket listening for incoming connections created via \texttt{create\allowbreak Insecure\allowbreak Rfcomm\allowbreak SocketToServiceRecord} and needs an explicit pairing of two devices with user acceptance. The second method instead allows to manage incoming connection created with \texttt{} that do not require pairing with user acceptance.\\

@@

\section{\textbf{Related work}}
Different existing applications try to mimic a surveillance system but none of them exploits all available sensors on the phone. Moreover no phone tracking application offers a way different from direct internet connectivity to send phone's position (no opportonistic communication).\\

\begin{itemize}
	\item \textbf{Motion Detector Pro}: motion detection only app
	\item \textbf{Sound Detector}: sound detection only app. Can take pictures if the alarm is triggered
	\item \textbf{Surveillance}: motion and sound detection. Missing accelerometer motion detection, position tracking, SMS alerting and opportunistic communication
	\item \textbf{Wheres My Droid}: phone tracking app. Beta support for camera shots. Missing intrusion detection and opportunistic communication

\end{itemize}

@@

\bibitem{}
B. Clifford Neuman and Theodore Ts'o (September 1994) Kerberos: An Authentication Service for Computer Networks. IEEE Communications 32. \\
\bibitem{}
S. Chita, N. Peterson, B.A. Shirazi, M. Bhadkamkar (March 2011) Home automation and security for mobile devices. PERCOM 2011. \\
\bibitem{}
I. Estevez-Ayres et al. (January 2011) Using android smartphones in a service-oriented video surveillance system. ICEE 2011. \\
\bibitem{}
Heming Pang et al. (June 2010) Research of android smart phone surveillance system. ICCDA 2010. \\
\bibitem{}
M. Mitchell (January 2011) BEAT: Bio-Environmental Android Tracking. RWS 2011. \\
\bibitem{}
G. Bianchi, P. Loreti, A. Trkulja (June 2012) Let me grab your App: Preliminary proof-of-concept design of opportunistic content augmentation. ICC 2012. \\
\bibitem{}
T. Hossmann, D. Schatzmann, P. Carta, F. Legendre (2012) Twitter in disaster mode: smart probing for opportunistic peers. MobiOpp 2012.\\
